### 2015-08-15 fundamentals/examples.tex
uses a table to better capture the parameters in bullet points.

The success of the \Cyclus simulator can be measured in many ways.  The most
compelling are demonstrations of fundamental simulation capability and of the
feasibility of the \Cyclus community-driven development model. Promising
growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
cycle simulator can advance in this community-driven development
paradigm. Additionally, simulation results for both once-through and more
complex recycling scenarios demonstrate that \Cyclus possesses the fundamental
fuel cycle simulation capabilities to contribute to the field.

@@

\begin{enumerate}
    \item Once through (no recycle)
    \item 1-pass \gls{MOX} recycle
    \item Infinite-pass \gls{MOX} recycle
\end{enumerate}

For each of these fuel cycles, a 1,100 month single-reactor \Cyclus simulation
was run in addition to a 10-reactor simulation with staggered refueling times.
As the number of staggered-cycle reactors increases the system converges
toward continuous material flow results.  \Cyclus flexibility allows this
transition to be examined.  The facilities used in these simulations are:

\begin{itemize}

>>>>

The success of the \Cyclus simulator can be measured in many ways.  The most
compelling are early successes of the community-driven development model and 
demonstrations of its fundamental simulation capabilities. Promising
growth of the \Cyclus ecosystem at multiple institutions indicates that a fuel
cycle simulator can advance in this community-driven development
paradigm. Additionally, simulation results for both once-through and more
complex recycling scenarios demonstrate that \Cyclus possesses the fundamental
fuel cycle simulation capabilities to contribute to the field.

@@

\begin{enumerate}
    \item No Recycle (once through)
    \item 1-pass \gls{MOX} Recycle
    \item Infinite-pass \gls{MOX} Recycle
\end{enumerate}

For each of these fuel cycles, a 1,100 month single-reactor \Cyclus simulation
was run in addition to a 10-reactor simulation with staggered refueling times.
As the number of staggered-cycle reactors increases the system converges
toward continuous material flow results.  \Cyclus flexibility allows this
transition to be examined.

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20000$ [kg HM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & fffers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table}

As described in Table \ref{tab:facconfigs}, the facilities used in these simulations are:
\begin{itemize}
